\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\Large Shiju Devarajan} & Email : \href{mailto:shijudevarajan@gmail.com}{shijudevarajan@gmail.com}\\
\href{https://shijudevarajan.github.io/}{https://shijudevarajan.github.io/} & Mobile : +1-646-764-1506 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Government Engineering College Idukki}{Kerala, India}
{Bachelor of Technology in Information Technology}{Aug. 2003 -- Aug. 2007}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{StayNTouch Inc}{Bethesda, MD}
{Software Engineer}{Nov 2018 - Present}
\resumeItemListStart
%
%\resumeItem{StayNTouch PMS}
%{A cloud-based solution designed and optimized for tablet computing and smartphones,
%leading to a more nimble and effective hotel staff while at the same time dramatically increasing %guest engagement.}
%
\resumeItemListEnd

% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
{QBurst Inc}{Chantily, VA}
{Associate Architect}{March 2017 - Oct 2018}

\resumeSubheading
{QBurst Technologies}{Trivandrum, Kerala}
{Associate Architect}{July 2016 - Feb 2017}

\resumeSubheading
{QBurst Technologies}{Trivandrum, Kerala}
{Lead Engineer}{June 2010 - June 2016}

\resumeSubheading
{Amskape Inc}{Cochin, Kerala}
{Software Engineer}{Aug 2008 - June 2010}

\resumeSubheading
{Ace Infotect Inc}{Trivandrum, Kerala}
{Software Trainee}{Sep 2007 - July 2008}

\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{StayNTouch PMS}
{A cloud-based solution designed and optimized for tablet computing and smartphones,
leading to a more nimble and effective hotel staff while at the same time dramatically increasing guest
engagement.}
\resumeSubItem{CustomMade}
{A Google Ventures company, is changing the way people shop by making
buying custom easier. They want to be an alternative to big box retailers by providing an online
marketplace that connects consumers with artisans across the country. They are creating a consumer
experience where consumers can connect with an artisan maker to co-create something unique.}
\resumeSubItem{SevaCall}
{Seva Call eliminates the time involved in using phone books and other resources to find the
perfect service provider and provides a much more efficient means of finding them. All the consumers
need to do is tell us what service you would like, when you want it and where you are located! Seva Call will then broadcast these details to local companies you have selected. Seva Call will connect you to companies instantly.}
\resumeSubItem{Kaboom}
{Kaboom's mission is to have a playground within walking distance of every child in the US
so that every child has easy access to a play area. Their aim is to build at least 150 playgrounds per year through the project called ODP (Our Dream Playground). To this end, they require a lot of funding. Through their website, they aim to attract communities to fund for their play ground projects and also empower communities to build play spaces of their own.}
\resumeSubItem{Springboard}
{SPRINGBOARD CDM is a comprehensive solution for managing and delivering mobile
content and applications. It provides a single solution permitting the service provider to manage and
deliver media assets via Web (Online).}
\resumeSubItem{Idealconsent}
{IdealConsent is a new and innovative approach patients can use to give consent. This
software helps increase medical education among patients, conversation between patients and their
physicians, and ultimately improves the process of informed consent where the outdated method of
written consent on paper has failed. This powerful tool for the healthcare industry will help organize
medical offices while giving patients full awareness of the procedures that they are consenting to do.}
\resumeSubItem{Purechart}
{PureChart is an intuitive anywhere, anytime dental enterprise software program, partnered with Medicaid to allow direct billing. }
\resumeSubItem{Redmine Meeting Calendar Plugin}
{This opensource Redmine plugin allows you to book meeting rooms and thence display it on a calendar interface.}
\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}